### 2020-06-29 manuscript/manuscript.rmd
minor changes to the text

In contrast, the phylogenetic signal of site-heterogenous models changed dramatically compared to the site-homogenous models. Although Ctenophora-sister also had the higher proportions of supporting genes with C60 models, we found that the phylogenetic signal decreases in many genes using C60 models compared to site-homogeneous models, especially in matrices from Ryan2013_est that nearly 30% of genes changed from strong to week signal ($\Delta$lnL<2) (Extended Data Fig. 3; Supplementary Table 4). In contrast to the C60 models, the phylogenetic signal largely increased in Poisson-CAT models and more importantly, the outgroup choice has a major effect of the distribution of phylogenetic signal (Extended Data Fig. 3). We found that support for Ctenophora-sister largely decreases and Porifera-sister increases (~ 20% of sampled gene partitions) when exclusive of more distantly related outgroups with the Poisson-CAT models (Supplementary Table 4). The results here are further corroborated by our phylogenomic analyses in BI, which the support of Porifera-sister generally increases in Holozoa and Choanimalia matrices.

@@

```{r figure_gene_composition,, fig.height = 6, fig.width = 10}

@@

```{r figure_phylogenetic_signal, fig.width=6, fig.height=12}

au_tests %>%
  unite(Matrix, c(manuscript, matrix, model)) %>%
  group_by(Matrix, result) %>%
  count() %>%
  group_by(Matrix) %>%
  mutate(percent = prop.table(n)) %>%
  ggplot(aes(x = Matrix, y = percent, fill = result)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("#E69F00", "#ebd196", "#a2e8d5", "#009E73")) +
    coord_flip() +
    theme(axis.text.y = element_blank(), axis.title.y = element_blank())

```
**Extended Data Fig. 3** The distribution of phylogenetic signal for two alternative topological hypotheses on the earliest-branching animal lineage with different models and outgroup choice in Philippe2009, Ryan2013 and Whelan2017_full matrices (with two outgroup sampling: Choanimalia and full matrices). The two alternative topological hypotheses are: Ctenophora-sister; T1 (Orange);Porifera-sister T2 (Green). Proportions of genes supporting each of two alternative hypotheses in the Philippe2009, Ryan2013_est and Whelan2017_full data matrices with differnet outgroups sampling and substitutional models. The GLS values for each gene in each data matrix are provided in Table S5. We considered a gene with an absolute value of log-likelihood difference of two as a gene with strong (|ΔlnL| > 2) or weak (|ΔlnL| < 2) phylogenetic signal.

>>>>

In contrast, the phylogenetic signal of site-heterogenous models changed dramatically compared to the site-homogenous models. Although Ctenophora-sister also had the higher proportions of supporting genes with C60 models, we found that the phylogenetic signal decreases in many genes using C60 models compared to site-homogeneous models, especially in matrices from Ryan2013_est that nearly 30% of genes changed from strong to week signal ($\Delta$|lnL|<2) (Extended Data Fig. 3; Supplementary Table 4). In contrast to the C60 models, the phylogenetic signal largely increased in Poisson-CAT models and more importantly, the outgroup choice has a major effect of the distribution of phylogenetic signal (Extended Data Fig. 3). We found that support for Ctenophora-sister largely decreases and Porifera-sister increases (~ 20% of sampled gene partitions) when exclusive of more distantly related outgroups with the Poisson-CAT models (Supplementary Table 4). These results here are further corroborated by our phylogenomic analyses in BI, which the support of Porifera-sister generally increases in Holozoa and Choanimalia matrices.

@@

```{r figure_gene_composition,, fig.height = 4, fig.width = 10}

@@

###```{r figure_phylogenetic_signal, fig.width=6, fig.height=12}

#au_tests %>%
#  unite(Matrix, c(manuscript, matrix, model)) %>%
#  group_by(Matrix, result) %>%
#  count() %>%
#  group_by(Matrix) %>%
#  mutate(percent = prop.table(n)) %>%
#  ggplot(aes(x = Matrix, y = percent, fill = result)) +
#    geom_bar(stat = "identity") +
#    scale_fill_manual(values = c("#E69F00", "#ebd196", "#a2e8d5", "#009E73")) +
#    coord_flip() +
#    theme(axis.text.y = element_blank(), axis.title.y = element_blank())

#```

![](figures/Figure_phylogenetic_signal.png)

**Extended Data Fig. 3** The distribution of phylogenetic signal for two alternative topological hypotheses on the earliest-branching animal lineage with different models and outgroup choice in Philippe2009, Ryan2013 and Whelan2017_full matrices (with two outgroup sampling: Choanimalia and full matrices). The two alternative topological hypotheses are: Ctenophora-sister; T1 (Orange);Porifera-sister T2 (Green). Proportions of genes supporting each of two alternative hypotheses in the Philippe2009, Ryan2013_est and Whelan2017_full data matrices with differnet outgroups sampling and substitutional models. The GLS values for each gene in each data matrix are provided in Table S5. We considered a gene with an absolute value of log-likelihood difference of two as a gene with strong (|ΔlnL| > 2) or weak (|ΔlnL| < 2) phylogenetic signal.
